An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-18 poly-embed-journal/poly-embed-journal.tex
start sec 3,6 reorg

To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Corollary~\ref{cor:representative-embeds-restriction}).
In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.

In Proposition~\ref{prop:embed-bayes-risks}, we show an equivalent condition to embedding, whose proof relies on the following Lemma about the Bayes risk of a ``restricted'' surrogate, shown here.
\begin{lemma}\label{lem:loss-restrict}
  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ be representative for $L$.
  % such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
  Then $L|_{\R_2}$ elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
  Moreover, $\risk{L}=\risk{L|_{\R_2}}$.
\end{lemma}
\begin{proof}
	Let $p\in\simplex$ be fixed throughout.
	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
	We now see $r \in \Gamma(p) \cap \R_2$.
	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

%\jessiet{Make Construction- not definition}
%\begin{definition}[$\Sc(L)$]\label{cons:rep-set}
%	Suppose a generic loss $L : \R \to \reals^\Y$ is given with polyhedral negative risk $-\risk{L}$.
%	Construct the set $\Sc(L)$ as follows:
%	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
%	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
%	Add $u$ to $\Sc(L)$, and repeat, iterating over each of $E_L$'s finitely many facets.
%\end{definition}

\raf{Something like this:}\\
Together, Lemma~\ref{lem:loss-restrict} and Proposition~\ref{prop:embed-bayes-risks} give the following useful tool for finding embeddings.
\begin{corollary}\label{cor:representative-embeds-restriction}
  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.\jessie{Type check: $\reals^d$ vs $\R$?}
\end{corollary}

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}

@@

\raf{Start w/ Lemma X}

@@

@@

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Corollary~\ref{cor:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
  Since $\Gamma|_\U$ is non-redundant (Definition~\ref{def:nonredundant-prop}) by a corollary of the assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

$3 \Rightarrow 1$:
Consider the loss $\ell := L|_\U$.
$\ell$ is a finite loss since $\U$ is finite, and by Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $\ell$.
As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.

@@

$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$. 
\raf{Use Cor 4 + 6 again, maybe uniqueness of full-dim level sets from Lemma}

@@

%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.

@@

%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.

@@

%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.

>>>>

To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}).
In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}.

\raf{Do we want this anymore?  We violate it right off the bat with Lemma~\ref{lem:loss-restrict}...}
Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.

A first step is a simple lemma showing that restricting a loss to only those reports in some representative set preserves the Bayes risk.
We will use this lemma throughout the paper.
\begin{lemma}\label{lem:loss-restrict}
  Let $L$ elicit $\Gamma:\simplex\toto\R_1$, and let $\R_2\subseteq\R_1$ be representative for $L$.
  % such that $\Gamma(p) \cap \R_2 \neq \emptyset$ for all $p\in\simplex$.
  Then $L|_{\R_2}$ elicits $\gamma:\simplex\toto\R_2$ defined by $\gamma(p) = \Gamma(p)\cap \R_2$.
  Moreover, $\risk{L}=\risk{L|_{\R_2}}$.
\end{lemma}
\begin{proof}
	Let $p\in\simplex$ be fixed throughout.
	First let $r \in \gamma(p) = \Gamma(p) \cap \R_2$.
	Then $r \in \Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$, so as $r\in\R_2$ we have in particular $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	For the other direction, suppose $r \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	By our assumption, we must have some $r^* \in \Gamma(p) \cap \R_2$.
	On the one hand, $r^*\in\Gamma(p) = \argmin_{u\in\R_1} \inprod{p}{L(u)}$.
	On the other, as $r^* \in \R_2$, we certainly have $r^* \in \argmin_{u\in\R_2} \inprod{p}{L(u)}$.
	But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(r^*)}$, and thus $r \in \argmin_{u\in\R_1} \inprod{p}{L(u)} = \Gamma(p)$ as well.
	We now see $r \in \Gamma(p) \cap \R_2$.
	Finally, the equality of the Bayes risks $\min_{u\in\R_1} \inprod{p}{L(u)} = \min_{u\in\R_2} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\R_2 \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

Lemma~\ref{lem:loss-restrict} leads to the following useful tool for finding embeddings.
\begin{proposition}\label{prop:representative-embeds-restriction}
  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
  If $L$ has a finite representative set $\U \subseteq \reals^d$, then $L$ embeds the discrete loss $L|_\U$.
\end{proposition}
\begin{proof}
  Let $\Gamma = \prop{L}$ and $\gamma = \prop{L|_\U}$.
  Define $\varphi : \U \to \U$ to be the identity embedding.
  Condition (i) of an embedding is trivially satisfied, as $L|_\U(u) = L(u)$ for all $u\in\U$.
  Now let $u\in\U$.
  From Lemma~\ref{lem:loss-restrict}, for all $p\in\simplex$ we have $u \in \gamma(p) \iff u \in \Gamma(p) \cap \U \iff u \in \Gamma(p)$.
  We conclude condition (ii) of an embedding.
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  \raf{Update notation here; been using $\U$ for a set of reports everywhere else}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. 
  For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
  Then $\Sc$ is representative for $L$.
  Proposition~\ref{prop:representative-embeds-restriction} now states that $L$ embeds $L|_{\Sc}$.
\end{proof}

@@

\subsection{Structure of polyhedral Bayes risks}
\raf{Lemma X}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

  $\Leftarrow$
  \btw{Commented out version relying on hyperplanes without power diagrams; it was incorrect - Jessie 1 June 21}
  Since $\U$ is a finite representative set, we know $L|_\U$ is embedded by $L$ in Proposition~\ref{prop:representative-embeds-restriction}.
  Therefore, $\Gamma := \prop{L}$ embeds $\Gamma|_\U := \prop{L|_\U}$ (see Definition~\ref{def:prop-embed} in \S~\ref{app:embed-props}).
  Since $\Gamma|_\U$ is non-redundant (Definition~\ref{def:nonredundant-prop}) by a corollary of the assumption, we can apply Proposition~\ref{prop:embed-trim}\jessiet{BTW: Forward ref}, $\U$ is a minimum representative set for $L$.
%  Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
%  This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.
%  
%  If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.
%  
%  Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
%  By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
%  As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%  
%  Now observe that 
%  $r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
%  Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.
%  
%  Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

@@

$3 \Rightarrow 1$:
Consider the loss $\ell := L|_\U$.
$\ell$ is a finite loss since $\U$ is finite, and by Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $\ell$.
As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.

@@

$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Proposition~\ref{prop:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$. 
\raf{Use Cor 4 + 6 again, maybe uniqueness of full-dim level sets from Lemma}

@@

%  We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Proposition~\ref{prop:representative-embeds-restriction}.

@@

%  %% If we show $ c \implies b$, we have $b \implies a$ as an version of Proposition~\ref{prop:representative-embeds-restriction}.

@@

%  % If $\R'$ is a minimum representative set, then we have the result by an analog of Proposition~\ref{prop:representative-embeds-restriction}.
